Interpretable Machine Learning

### 2018-05-30 talk-40min.Rmd
continues talk

## Step 2: Throw ML on your data
```{r learn}
library('mlr')
set.seed(42)
task = makeRegrTask(data = survey.dat, target = 'CompensationAmount')
lrn = makeLearner('regr.randomForest')
mod = train(lrn, task)
```
## Step 3: Profit. {.center}

@@

@@

@@

@@

### Interpretable Models

TODO: Graphic with schematic interpretable model

### Interpretable Models

TODO: Graphic with tree+if-then-rules+decision tree

## Model-agnostic methods
TODO: Graphic with schematic Model-agnostic methods

@@

## Model-specific methods
TODO: Graphic with schematic Model-specific methods

TODO: add images from papers

>>>>

## Step 2: Throw ML on your data
```{r learn}
library('mlr')
set.seed(42)
task = makeRegrTask(data = survey.dat, target = 'CompensationAmount')
lrn = makeLearner('regr.randomForest')
mod = train(lrn, task)
```

TODO: Insert image

## Step 3: Profit. {.center}

@@

## The Problem

- Opaque decision making by machine learning algorithms
- Examples: AI doctor, self-driving cars, creditworthiness
- Trust as a user: Should I start severe therapy, because the machine said so?
- Debugging as a practitioner: Why did the algorithm miss-classify sample X? Did it learn generalizable features?

![](images/black-box.png)

@@

- Debugging
- Increasing trust

### Example: Doctor and ML

### Example: Predictive CV screening

- Nasty feedback loops
- Biased data
- Proxies instead of causality
-

## Example:

@@

Things that work well. 
Well defined problems

## Example: Digit recognition

![](images/mnist.jpeg)

@@

## Interpretable Models

![](images/black-box.png)

## Interpretable Models

![](images/white-box.png)

## Interpretable Models

- Decision trees
- Decision rules
- Generalized regression models
- ...

![](images/black-box.png)

![](images/specific-black-box.png)

TODO: add images from papers
## Model-agnostic methods
![](images/black-box.png)

## Model-agnostic methods
![](images/agnostic-black-box.png)

@@

## Data-focused methods
![](images/black-box.png)

## Data-focused methods
![](images/data-box.png)

## Data-focused methods

- Prototypes: What is the prototype of a certain class
- Criticisms: Which data points are unusual for a certain class. 
- Counterfactuals: What do I need to change for an instance to change the prediction?
- Anchors: What features do I have to anchor to keep prediction the same?

TODO: Cite

## Outcomes of interpretability method:

- Model
- Data point
- Interpretable unit (like a weight)
- Summary statistic for a feature
